A Dependently Typed Multi-Stage Calculus\thanks{Supported by organization x.}

### 2019-05-17 main.tex
Delete one technical point.
Wrote the first line!!!!

The main technical points of this paper are how to deal with Cross Stage Persistence of multi-stage calculuses which allows using a value in quoted code in a dependent type system.

The first point is CSP in kinding rules.
$\lambda^{\TW\%}$ includes kinding rules because dependent types need them
but the relationship between kinds and stages wasn't clear.

The second point is CSP in equivalence rules.
Parameters of dependent types may contain cross-staged terms.
We give reasonable equivalence rules to handle them.

@@

\section{Formal Definition of \LMD}
\subsection{Syntax}

\begin{align*}
    \textrm{Terms} && M,N,L,O,P & ::= x \mid \lambda x:\tau.M\ \mid M\ M \mid \TB_\alpha M 
    \mid \TBL_\alpha M \mid \Lambda\alpha.M \mid M\ \epsilon \mid \%_\alpha M\\ 
    \textrm{Types} && \tau,\sigma,\rho,\pi,\xi & ::= X \mid \Pi x:\tau.\tau \mid \tau\ M \mid \TW_{\alpha} M \mid \F\alpha.\tau \\
    \textrm{Kinds} && K,J,I,H,G & ::= * \mid \Pi x:\tau.K\\
    \textrm{Contexts} && \Gamma & ::= \phi \mid 
    \Gamma,x:\tau @A\ (x\not\in\textrm{FV}(\G)) \mid 
    \Gamma,X::K @A\ (X\not\in \textrm{FV}(\G))\\
    \textrm{Transition variables} && & \alpha,\beta,\gamma, \dots \\
    \textrm{Transition} && & A,B,C,\dots \\
    \textrm{Variables} && & x,y,z,\dots \\
    \textrm{Type variables} && & X,Y,Z,\dots \\
\end{align*}

@@

\subsection{Type System}
\subsubsection{Equivalence Rules}

>>>>

The main technical points of this paper are how to deal with Cross Stage Persistence of multi-stage calculuses which allows using a value in quoted code in a dependent type system.
Especially, handling CSP in equivalence rules of dependent types wasn't clear.
Parameters of dependent types may contain cross-staged terms.
We give reasonable equivalence rules to handle them.

@@

\section{Formal Definition of \LMD}

In this section, we present \LMD in detail. we will define syntax, full reduction, type system including type equivalence rules, values, and evaluation context which take stages into account.
In the next section, we will discuss on properties of \LMD.

\subsection{Syntax}

\begin{align*}
    \textrm{Terms} && M,N,L,O,P & ::= c \mid x \mid \lambda x:\tau.M\ \mid M\ M \mid \TB_\alpha M 
    \mid \TBL_\alpha M \mid \Lambda\alpha.M \mid M\ \epsilon \mid \%_\alpha M\\ 
    \textrm{Types} && \tau,\sigma,\rho,\pi,\xi & ::= X \mid \Pi x:\tau.\tau \mid \tau\ M \mid \TW_{\alpha} M \mid \F\alpha.\tau \\
    \textrm{Kinds} && K,J,I,H,G & ::= * \mid \Pi x:\tau.K\\
    \textrm{Contexts} && \Gamma & ::= \phi \mid  \Gamma,x:\tau@A\ (x\not\in\textrm{FV}(\G)) \\
    \textrm{Signature} && \Sigma & ::= \phi \mid X::K \mid c:\tau \\
    \textrm{Transition variables} && & \alpha,\beta,\gamma,... \\
    \textrm{Transition} && & A,B,C,... \\
    \textrm{Variables} && & x,y,z,... \\
    \textrm{Type variables} && & X,Y,Z,... \\
\end{align*}

@@

\subsection{Type System}
\subsubsection{Type Equivalence Rules}
